Appendix 2 - Fitting proposed path models using the C-statistic

### 2015-05-21 search4superspreaders.Rmd
Added titles to some of the code chunks

## Stems in the 99th Percentile 3+ Years
```{r echo=FALSE}
dt <- table(d$tag)
d2 <- subset(d, tag %in% names(dt[dt > 2]))
```

@@

```{r echo=FALSE, eval=FALSE}
#summary(d)
#str(d)
#d <- droplevels(d)
#length(unique(d$plot))
#length(unique(d$tag))

>>>>

## Stems in the 99th Percentile 3+ Years
```{r Stems repeated 3+ years, echo=FALSE}
dt <- table(d$tag)
d2 <- subset(d, tag %in% names(dt[dt > 2]))
```

@@

```{r Conditional subsetting data, echo=FALSE, eval=FALSE}
#summary(d)
#str(d)
#d <- droplevels(d)
#length(unique(d$plot))
#length(unique(d$tag))
